Hydrodynamics of a Semi-permeable Vesicle Under Flow and Confinement

### 2020-12-29 vesicle_code/docs/permeableVes/main.tex
yny

%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
%Physics}
\title{Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a]{Bryan Quaife}
\author[a]{Ashley Gannon}
\author[b,1]{Y.-N. Young}

\affil[a]{Department of Scientific Computing, Florida State University}
\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
Technology}

>>>>

%\title{Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and
%Physics}
\title{Hydrodynamics of a  Semi-permeable Vesicle Under Flow and Confinement}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a]{Bryan Quaife}
\author[a]{Ashley Gannon}
\author[b]{Howard A. Stone}
\author[c,1]{Y.-N. Young}

\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 33306}
\affil[b]{Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
\affil[c]{Department of Mathematical Sciences, New Jersey Institute of
Technology, Newark, NJ 07102}
